Analysis methods for characterizing the climate sensitivity of annual growth and woody productivity using tree-rings

### 2020-03-16 methods/analysis_methods.Rmd
update methods

[Helcoski et al. 2019](https://nph.onlinelibrary.wiley.com/doi/abs/10.1111/nph.15906), [GitHub repo with full results](https://github.com/SCBI-ForestGEO/climate_sensitivity_cores) analyzed climate sensitivity using traditional dendro methods and gave a reliable (as far as we know!) picture of climate sensitivity at SCBI. From our explorations of other analysis methods on the same data, it seems that pulling out a reliable climate signal *requires* indivdidual-level detrending of cores. Our attempt to do this with raw growth data, using climwin and a mixed effects model to account for DBH and year, resulted in weak or absent climate correlations that didn't align with Helcoski results. However, if we fit splines to individual core sequences and then analyze these data in *climwin*, we get results that are generally very consistent with Helcoski (except that they don't pull out an opposite signal from the previous growing season).

>>>>

[Helcoski et al. (2019)](https://nph.onlinelibrary.wiley.com/doi/abs/10.1111/nph.15906), [(GitHub repo with full results)](https://github.com/SCBI-ForestGEO/climate_sensitivity_cores) analyzed climate sensitivity using traditional dendro methods and gave a reliable (as far as we know!) picture of climate sensitivity at SCBI. From our explorations of other analysis methods on the same data, it seems that pulling out a reliable climate signal *requires* indivdidual-level detrending of cores. Our attempt to do this with raw growth data, using climwin and a mixed effects model to account for DBH and year, resulted in weak or absent climate correlations that didn't align with Helcoski results. However, if we fit splines to individual core sequences and then analyze these data in *climwin*, we get results that are generally very consistent with Helcoski (except that they don't pull out an opposite signal from the previous growing season).
